Predicting Political Support in the United States

### 2024-03-12 output/paper.qmd
Start Paper

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

@@

# Results

# Discussion

# Appendix

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

#### Workspace setup ####
library(knitr)
library(tidyverse)

```

@@

```{r}

cm <- c('raceWhite' = 'White',
        'raceNative American' = 'Native American', 
        'raceMultiracial' = 'Multiracial',
        'raceMiddle Eastern' = 'Middle Eastern',
        'raceHispanic' = 'Hispanic',
        'raceBlack' = 'Black',
        'genderMale' = 'Male')

modelsummary(
  list(
    "Support Biden" = political_preferences_gender_race
  ),
  statistic = "mad"
  )

modelplot(political_preferences_gender_race, conf_level = 0.9, coef_map = cm) + labs(x = "90 per cent credibility interval")
```

## Results

## Discussion

## Conclusion

## Appendix

## References
